Visually pleasing knot projections

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

Figure 4 caption: Much of the explanation of "7 3" versus "3 7" is
already in the main text.

Page 8, Line 60: "Why 64 real variables"?  What are they?  How does
this agree with "R50" on page 6 ?

Figure 7: Where does the spiky artifact in the upper right lobe come
from?  \textcolor{blue}{\\I see nothing in figure 7 that could be so
  described.  I expect this is a rendering issue, if so it will be
  sorted out at proofreading stage.\\ \\}

Page 12, Line 52: ``...a rotationally symmetric" should be ``... a knot with
pure cyclic rotational symmetry, rather than dihedral symmetry"
  \textcolor{blue}{Done\\ \\}

Figure 9: Why did the user choose to place three nodes on the outer
lobes, rather than only two? - Was this easier to express the desired
symmetry??  \textcolor{blue}{\\Sort of.  Having more nodes allows for
  finer and more sophisticated control over the path, and having too
  few nodes results in a displeasing, unnatural flabby configuration.
  On the other hand, having too many nodes results in the optimization
  routine thrashing and failing to converge.  In this case it is
  desirable to have an odd number of nodes: 12,4,16,8,20 are
  constrained by the symmetry routine to be exactly on one of the five
  lines of symmetry, and to intersect its line at exactly $90^\circ$.
  Frankly the choice of number of nodes has been troublesome in the
  development of the software.  Perhaps this issue is of interest to
  the JMA readership and I have added a brief sentence discussing it
  to the manuscript: ``Note that increasing the number of nodes
  provides more control over the path at the expense of a more
  difficult optimization process".  Also, at the discussion of Figure
  9: ``from Figure 9 we see that these nodes are constrained to lie on
  one of the five lines of symmetry, cutting it at $90^\circ$".\\ \\}

Page 16, Line 47: "The strands exert a couple but no force on one
another."    Lengthy discussions should be relegated to the main
text, rather than be in figure captions.

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

Figure 7: Where does the spiky artifact in the upper right lobe come
from?  \textcolor{blue}{\\I see nothing in figure 7 that could be so
  described.  I expect this is a rendering issue, if so it will be
  sorted out at proofreading stage.\\ \\}

Page 12, Line 52: ``...a rotationally symmetric" should be ``... a knot with
pure cyclic rotational symmetry, rather than dihedral symmetry"
  \textcolor{blue}{Done\\ \\}

Figure 9: Why did the user choose to place three nodes on the outer
lobes, rather than only two? - Was this easier to express the desired
symmetry??  \textcolor{blue}{\\Sort of.  Having more nodes allows for
  finer and more sophisticated control over the path, and having too
  few nodes results in a displeasing, unnatural flabby configuration.
  On the other hand, having too many nodes results in the optimization
  routine thrashing and failing to converge.  In this case it is
  desirable to have an odd number of nodes: 12,4,16,8,20 are
  constrained by the symmetry routine to be exactly on one of the five
  lines of symmetry, and to intersect its line at exactly $90^\circ$.
  Frankly the choice of number of nodes has been troublesome in the
  development of the software.  Perhaps this issue is of interest to
  the JMA readership and I have added a brief sentence discussing it
  to the manuscript: ``Note that increasing the number of nodes
  provides more control over the path at the expense of a more
  difficult optimization process".  Also, at the discussion of Figure
  9: ``from Figure 9 we see that these nodes are constrained to lie on
  one of the five lines of symmetry, cutting it at $90^\circ$".\\ \\}

Page 16, Line 47: ``The strands exert a couple but no force on one
another."  Lengthy discussions should be relegated to the main text,
rather than be in figure captions \textcolor{blue}{\\Done.  This
  discussion is relocated to the main text as suggested.\\ \\}

### 2023-01-31 inst/jma_knot.tex
fixes #98

There now follows a selection of pleasing knot diagrams taken from
datasets provided with the package, illustrating the relative ease
with which knot diagrams may be created and optimized.
Figure~\ref{two_trefoil_knots} shows and compares two plausible
schemes for rendering a trefoil.  Figure~\ref{perko_AB} shows two
forms of a 10-crossing knot once erroneously considered to be
topologically distinct; figure~\ref{orn20} shows an ornamental knot
with exact five-fold symmetry (but not dihedral symmetry); and
figure~\ref{all8} shows all prime knots with eight or fewer crossings,
following Rolfsen~\cite{rolfsen1976}.  The package includes all knots
to nine crossings.

\begin{figure}[h]
  \centering  
  % To create file "two_trefoil_knots_post_inkscape.pdf" (which is
  % stored on the repo), run knotter.R, which makes (among other
  % things) two_trefoil_knots.pdf.  Edit this in inkscape [make a
  % mirror image, then change the colours and finally use the raise
  % and lower tools to put everything in the right order]
    \includegraphics[width=10cm]{two_trefoil_knots_post_inkscape.pdf}
    \caption{Two trefoil \label{two_trefoil_knots} knots.  Left,
      optimized as per the {\tt knotR} package techniques documented
      here; right, constructed from arcs of circles constrained to
      cross at right angles.  The strands exert a couple but no force
      on one another.  Mirror symmetry and threefold rotational
      symmetry are imposed.  Elementary trigonometry shows that the
      radii of the inner and outer loops are
      $\operatorname{cosec}(\pi/12)=\sqrt{6}+\sqrt{2}$ and
      $\sec(\pi/12)=\sqrt{6}-\sqrt{2}$ respectively.  The curvature
      thus has a displeasing discontinuity at a node which interrupts
      the visual continuity there, especially the understrand}
\end{figure}

>>>>

There now follows a selection of pleasing knot diagrams taken from
datasets provided with the package, illustrating the relative ease
with which knot diagrams may be created and optimized.
Figure~\ref{two_trefoil_knots} shows and compares two plausible
schemes for rendering a trefoil: optimized as per the {\tt knotR}
package techniques documented here; compared with a trefoil knot
constructed from arcs of circles constrained to cross at right angles.
In the circular-arc trefoil, the strands exert a couple but no force
on one another.  Mirror symmetry and threefold rotational symmetry are
imposed.  Elementary trigonometry shows that the radii of the inner
and outer loops are $\operatorname{cosec}(\pi/12)=\sqrt{6}+\sqrt{2}$
and $\sec(\pi/12)=\sqrt{6}-\sqrt{2}$ respectively.  We see the
disadvantages of placing nodes at crossing points.

Figure~\ref{perko_AB} shows two
forms of a 10-crossing knot once erroneously considered to be
topologically distinct; figure~\ref{orn20} shows an ornamental knot
with exact five-fold symmetry (but not dihedral symmetry); and
figure~\ref{all8} shows all prime knots with eight or fewer crossings,
following Rolfsen~\cite{rolfsen1976}.  The package includes all knots
to nine crossings.

\begin{figure}[h]
  \centering  
  % To create file "two_trefoil_knots_post_inkscape.pdf" (which is
  % stored on the repo), run knotter.R, which makes (among other
  % things) two_trefoil_knots.pdf.  Edit this in inkscape [make a
  % mirror image, then change the colours and finally use the raise
  % and lower tools to put everything in the right order]
    \includegraphics[width=10cm]{two_trefoil_knots_post_inkscape.pdf}
    \caption{Two trefoil \label{two_trefoil_knots} knots.  Left,
      optimized as per the {\tt knotR} package techniques documented
      here; right, constructed from arcs of circles constrained to
      cross at right angles.    On the right, the curvature
      has a displeasing discontinuity at a node which interrupts
      the visual continuity there, especially the understrand}
\end{figure}
